Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-06 manuscript.Rmd
typo

We have developed a workflow that achieves long-term and cross-platform computational reproducibility of scientific data analyses.
It leverages established tools and practices from software engineering and rests on four pillars that address the aforementioned causes of non-reproducibility: [@Peikert2019]:

>>>>

We have developed a workflow that achieves long-term and cross-platform computational reproducibility of scientific data analyses.
It leverages established tools and practices from software engineering and rests on four pillars that address the aforementioned causes of non-reproducibility [@Peikert2019]:
